Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
style
AB-review: style

Filter methods can be grouped into classes: Correlation based, entropy based, linear and non-linear methods.
It is important to not give certain classes too much weight in the ensemble as otherwise the final result will be biased towards these.
In this study this was taken care of by checking the rank correlations (Spearman's correlation) of the generated feature rankings of all methods against each other.
In case pairs of filters with a correlation above 0.9 were discovered, only one of these was included into the ensemble filter.
By this we ensured that the ensemble filter is not biased towards a certain group of methods yielding highly similar rankings.

@@

\begin{itemize}
	\item univariate/multivariate (scoring based on a single variable / multiple variables)
	\item linear/non-linear (calculation of linear/non-linear interaction terms)
	\item entropy/correlation (scoring based on derivations of entropy or correlation based approaches)
\end{itemize}

>>>>

Filter methods can be grouped into classes: Correlation-based, entropy-based, linear and non-linear methods.
It is important to not give certain classes too much weight in the ensemble as otherwise the final result will be biased towards these.
In this study this was taken care of by checking the rank correlations (Spearman's correlation) of the generated feature rankings of all methods against each other.
In case pairs of filters with a correlation above 0.9 were discovered, only one of these was included into the ensemble filter.
By this we ensured that the ensemble filter is not biased towards a certain group of methods yielding highly similar rankings.

@@

\begin{itemize}
	\item univariate/multivariate (scoring based on a single variable / multiple variables)
	\item linear/non-linear (calculation of linear/non-linear interaction terms)
	\item entropy/correlation (scoring based on derivations of entropy or correlation-based approaches)
\end{itemize}
